% !TEX program = xelatex

\documentclass[10pt, a4paper]{article}

% Packages
\usepackage[a4paper,margin=1.25cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[pdfpagelabels=false,hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{amssymb}

\hypersetup{allcolors=black}
\renewcommand{\labelitemi}{\textcolor[gray]{0.2}{--}}

% Page formatting
\pagestyle{empty}
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% ---------- Fonts ----------
% Headings — Playfair
\newfontfamily\headingfont{PlayfairDisplay-Regular.ttf}[
  Path=fonts/,
  BoldFont       = PlayfairDisplay-Bold.ttf,
  ItalicFont     = PlayfairDisplay-Italic.ttf,
  BoldItalicFont = PlayfairDisplay-BoldItalic.ttf
]

% Body — Roboto
\setmainfont{Roboto-VariableFont.ttf}[
  Path=fonts/,
  ItalicFont = Roboto-Italic-VariableFont.ttf,
  UprightFeatures     = {Weight=400},
  ItalicFeatures      = {Weight=400},
  BoldFeatures        = {Weight=600},
  BoldItalicFeatures  = {Weight=600}
]

% Colors
\definecolor{sectionblue}{RGB}{70, 90, 130}
\definecolor{ruleblue}{RGB}{70, 90, 130}

% Section formatting
\titleformat{\section}
  {\small\bfseries\scshape\color{sectionblue}\centering\letterspacing}
  {}{0em}{}
  [\vspace{-4pt}\color{ruleblue}\titlerule]

\titlespacing{\section}{0pt}{6pt}{4pt}

% Redefine section with colored background bar
\usepackage{tcolorbox}
\tcbuselibrary{skins}

% ---------- Commands ----------
\newcommand{\headingbold}{\headingfont\bfseries}
\newcommand{\headingregular}{\headingfont\mdseries}

\newcommand{\cvsection}[1]{%
  \vspace{4pt}
  \begin{tcolorbox}[
    colback=sectionblue!15,
    colframe=sectionblue!15,
    sharp corners,
    boxrule=0pt,
    left=0pt, right=0pt,
    top=2pt, bottom=2pt
  ]
  \centering\small\headingfont\bfseries\scshape\color{sectionblue}\MakeUppercase{#1}
  \end{tcolorbox}
  \vspace{4pt}
}

\newcommand{\role}[4]{% #1=Company, #2=Title, #3=Location, #4=Dates
  \noindent
  \begin{tabularx}{\textwidth}{p{3.55cm} X r}
    \headingbold#1 & $\cdot$\quad{\headingregular\small#2} & 
    {\color[gray]{0.4}\headingregular\small#3\ \quad$\cdot$\quad #4} \\
  \end{tabularx}
}

\newcommand{\earlyrole}[4]{% #1=Company, #2=Title, #3=Location, #4=Dates
  \noindent
  \begin{tabularx}{\textwidth}{p{3.55cm} X r}
    \headingbold#1 & $\cdot$\quad{\headingregular\small#2} & 
    {\color[gray]{0.4}\headingregular\small#3\ \quad$\cdot$ \makebox[1.85cm][r]{#4}} \\
  \end{tabularx}
}

\newcommand{\education}[4]{% #1=Company, #2=Title, #3=Location, #4=Dates
  \noindent
  \begin{tabularx}{\textwidth}{l X r}
    \headingbold#1 & $\cdot$\quad{\headingregular\small#2} & 
    {\color[gray]{0.4}\headingregular\small#3\ \quad$\cdot$ \makebox[1.85cm][r]{#4}} \\
  \end{tabularx}
}

% Checkmark command
\newcommand{\cmark}{\checkmark}

% Hyperlink setup
\hypersetup{
  colorlinks=true,
  urlcolor=sectionblue,
  linkcolor=sectionblue
}

\begin{document}

%---------- HEADER ----------
\begin{center}
  {\Huge\headingfont\bfseries\color{sectionblue}CAIUS EHMKE}\\[4pt]
  
  \vspace{6pt}
  
  \fontsize{7.75pt}{9.25pt}
  \selectfont NZ Permanent Resident
  \enspace $\cdot$ \enspace Kapiti, Wellington
  \enspace $\cdot$ \enspace (+31) 62 855 8580
  \enspace $\cdot$ \enspace cehmke91@gmail.com
  \enspace $\cdot$ \enspace \href{https://linkedin.com/in/cehmke91}{linkedin.com/in/cehmke91}
  \enspace $\cdot$ \enspace \href{https://github.com/c3hmke}{github.com/c3hmke} 
\end{center}

\vspace{2pt}
{\color{ruleblue}\hrule height 1.5pt}
\vspace{2pt}

%---------- TITLE ----------
\begin{center}
  \headingfont\bfseries\scshape senior software engineer \quad\textbar\quad data-intensive systems design \& legacy modernisation
\end{center}
\vspace{2pt}

%---------- SUMMARY ----------
\color[gray]{0.2}
With 10 years of experience, I bring strong expertise in system design, APIs, data modelling, and legacy modernisation 
with a focus on replacing ageing systems with modern, maintainable architectures that teams can actually build on. 
I take ownership of complex problem spaces and deliver pragmatic, reliable solutions across the full development lifecycle.
\vspace{4pt}

%---------- SKILLS ----------
\cvsection{Skills}
\begin{tabular}{@{} p{0.24\textwidth} p{0.24\textwidth} p{0.24\textwidth} p{0.24\textwidth} @{}}
  C\# / .NET     & API Design            & PostgreSQL / MySQL     & Docker \\
  PHP (Laravel)  & Distributed Systems   & Relational Modelling   & CI/CD \\
  JS (Node, Vue) & System Design         & Schema \& Migrations   & Logging \& Monitoring \\
  RabbitMQ       & Service Decomposition & Redis / Object Storage & Event-Driven Design \\
\end{tabular}

%---------- EXPERIENCE ----------
\cvsection{Experience}

\role{Sr. Software Engineer}{BIT B.V.}{Ede, Netherlands}{2023 \textendash\hspace{1pt} Present}
\begin{itemize}
  \color[gray]{0.2}
  \item Co-designed the service-federation protocol at the core of ECOFED, an EU project enabling independent cloud providers to host each other's services across organisational boundaries, and collaborated with a cross-company team to evolve it further
  \item Modernised a 30-year-old PHP platform by migrating to C\# and introducing an API layer that allowed the legacy system to be gutted incrementally, with Entity Framework abstracting the underlying database problems.
  \item Cleared a 10-year feature backlog on a legacy internal platform by replacing an undocumented, organically grown codebase with a maintainable architecture, enabling engineers to deliver new features consistently.
  \item Took ownership of a stalled access control project for a data centre environment, redesigning and building a \\distributed system that enforces visitor schedules by disabling access badges outside of announced visits.
  \item Overhauled the offer and billing workflow, integrating sales, accounting, and invoicing systems to reduce manual work for the sales team by 80\%.
  \item Built the supporting foundations for ongoing renewal, including CI/CD pipelines, raw SQL migration tooling, and a frontend toolkit to allow the existing UI to be replaced piece by piece. 
  \item Acted as a frequent mentor and technical sounding board for team members, supporting junior and mid-level \\engineers in their development and helping senior engineers pressure-test their ideas.
\end{itemize}
\vspace{4pt}

\role{Software Engineer}{Copernica B.V.}{Amsterdam, Netherlands}{\hspace{0.95cm}2022}
\begin{itemize}
  \color[gray]{0.2}
  \item Delivered incremental improvements and fixes across internal work-tracking systems, focusing on usability, \\responsiveness, and reliability.
  \item Investigated and resolved issues across a legacy codebase, often working from limited documentation and existing behaviour.
\end{itemize}
\vspace{4pt}

\role{Software Engineer}{Atabix Solutions B.V.}{Amsterdam, Netherlands}{2020 \textendash\hspace{1pt}2021}
\begin{itemize}
  \color[gray]{0.2}
  \item Led back-end design and delivery across several client projects, including a time tracking and invoicing platform, an inventory management system, and a temp worker staffing app.
  \item Delivered data-intensive B2B systems including a time tracking and invoicing platform, an inventory management system, and a temp worker staffing app.
  \item Laid the foundational work for what would later become the company's ERP platform.
\end{itemize}
\vspace{4pt}

\earlyrole{Software Engineer}{comscore B.V.}{Amsterdam, Netherlands}{2019}
\earlyrole{Software Engineer}{Signify Ltd.}{Wellington, New Zealand}{2018}
\earlyrole{Jr. Software Engineer}{Common Ledger Ltd.}{Wellington, New Zealand}{2016 \textendash\hspace{1pt} 2018}


%---------- EDUCATION ----------
\cvsection{Education}
\education{BIS Multimedia, Computer Science}{University of Pretoria}{Pretoria, South Africa}{2013 \textendash\hspace{1pt} 2015}

\end{document}